An Extension of LTL with Rules\\ and its Application to Runtime Verification

### 2019-02-02 rule-ltl.tex
fixing problems
Updates from ShareLaTeX

Addition of relations to temporal databases is done
for aggregation~\cite{Libkin}, where relations are
calculated, based on the current state, and are used for further calculating
functions (sums, maxima) over the sequence of states. Aggregations were also used in the runtime verification tool 
{\sf MonPoly}~\cite{agrebasin}.
%
% --- other less directly related work: ---
%
Numerous other systems have been produced for monitoring
execution traces against formal specifications. 
These include e.g. \cite{Meredith2011} \cite{larva} \cite{Reger2015} \cite{halle-beepbeep-ieee-12} \cite{LOLA}.

@@

\begin{itemize}
\item{P} restricts to {\em past} temporal operators.
\item{F} allows first-order quantification over
variables and relations over variables and constants.
\item{Q} adds quantification over predicates (for the propositional versions)
or over relations (for the first-order version). These objects can have different values at different states.
\item{E} allows extending the objects that occur in the input with
new auxiliary predicates (for the propositional versions) or relations (for the first-order cases).
\end{itemize}

>>>>

Addition of relations to temporal databases is done
for aggregation~\cite{Libkin}, where relations are
calculated, based on the current state, and are used for further calculating
functions (sums, maxima) over the sequence of states. Aggregations were also used in the runtime verification tool 
{\sf MonPoly}~\cite{agrebasin}.
%
% --- other less directly related work: ---
%
Numerous other systems have been produced for monitoring
execution traces against formal specifications. 
These include e.g. \cite{Meredith2011,larva,Reger2015,halle-beepbeep-ieee-12,LOLA}.

@@

\begin{itemize}
\item{P} restricts to {\em past} temporal operators.
\item{F} allows first-order quantification over
variables and relations over variables and constants. This is referred to as {\em static} quantification.
\item{Q} adds quantification over predicates (for the propositional versions)
or over relations (for the first-order version). These objects can have different values at different states. This is referred to as {\em dynamic} quantification.
\item{E} allows extending the objects that occur in the input with
new auxiliary predicates (for the propositional versions) or relations (for the first-order cases).
\end{itemize}

\klaus{You above introduce some concepts before they really are explained. I wonder whether the reader will understand. Specifically the E, but also the Q. Why not just introduce as we go along?}
